On the probability of finding nonphysical solutions through shadowing\tnoteref{1}

### 2021-04-23 main_els.tex
Add refs for attractor crises

\reviewerOne{
At the same time, the set of all periodic solutions is a dense subset of the attractor. That is,}

>>>>

\reviewerOne{
At the same time, families of periodic solutions have been well-studied for some problems}\cite{henon3body}.\reviewerOne{The set of all unstable periodic orbits have been recognized as the ``skeleton'' of the chaotic attractor \cite{cvitanovic1} forming a dense subset of the attractor and providing an alternative characterization of the SRB distribution \cite{llave}. This implies that ergodic/ensemble averages with respect to the SRB distribution are also weighted averages along the set of periodic orbits.} \reviewerOne{The significance of the set of unstable periodic orbits extends even further as it can be used to compute dynamical invariants such as entropy and Lyapunov dimension \cite{grebogi1}\cite{cvitanovic1}. A quantity of great mathematical interest is the dynamical determinant (see \cite{baladi-book} for a recent review), which is computed as a weighted sum over all periodic orbits. The zeros of the dynamical determinant have a one-to-one correspondence with the slowest decay rates of correlations between observables \cite{baladi-book}. This connection has been exploited both in mathematical as well as physical studies of the distribution of energy levels and resonances in quantum scattering \cite{semyonZworski}\cite{berry}\cite{cvitanovic2005chaos}. Furthermore, theoretical and numerical studies have attributed cataclysmic changes in the shape and position of the attractor in response to small parameter changes, known as attractor crises \cite{grebogi1}, to the emergence of tangencies between the stable and unstable manifolds along periodic orbits.}
